% CV LaTeX — Ouahabi Benhenni (English)
\documentclass[11pt,a4paper,sans]{moderncv}

% Style and colors
\moderncvstyle{banking}
\moderncvcolor{grey}

% Encoding and language
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}

% Force symbols icons to avoid fontawesome5
\moderncvicons{symbols}

% Layout
\usepackage[scale=0.90]{geometry}
\setlength{\hintscolumnwidth}{3.1cm}
\renewcommand*{\namefont}{\fontsize{26}{28}\bfseries\upshape}
\renewcommand*{\titlefont}{\fontsize{12}{14}\mdseries\upshape}

% Personal information
\name{Ouahabi}{Benhenni}
\title{AI Software Engineer · Computer Vision \& Biomedical AI}
\address{Boumerdès, Algeria}{}{ }
\phone[mobile]{+213 6 76 95 79 17}
\email{Ouahabi.benhenni.fs@univ-boumerdes.dz}
\homepage{ouahabi-benhenni.web.app}
\social[linkedin]{ouahabi-benhenni-a28bb5155}
\social[github]{Greyma}

\begin{document}
\makecvtitle

% AWARDS — highlighted at the top
\section{Awards \& Distinctions}
\cvitem{2025}{\textbf{1\textsuperscript{st} place} — National AI Competition Algeria-Tunisia (DevUp Boumerdès / Univ.\ of Tébessa): medical computer vision project using Deep Learning.}

% PROFILE
\section{Profile}
\cvitem{}{AI Software Engineer with 5+ years of hands-on delivery — from state-institution software during BTS to genomic AI pipelines at Institut Pasteur, through 10K+ user platforms and real-time systems under production load. Specializing in Computer Vision, Biomedical AI, and distributed systems. Experienced in microservices architecture, technical mentoring, and Agile team collaboration.}

% SKILLS
\section{Skills}
\cvitem{Languages}{Python, JavaScript, Java, C++, C\#, SQL, PHP}
\cvitem{AI / ML / DL}{PyTorch, TensorFlow, Keras, Scikit-Learn, OpenCV, Ultralytics, HuggingFace Transformers}
\cvitem{Architectures}{CNN, U-Net, YOLOv8, Vision Transformers, Mask R-CNN, RNN, Nucleotide Transformer}
\cvitem{LLM / GenAI}{LangChain, LangGraph, LLM agents, RAG, FAISS, ONNX}
\cvitem{Backend}{FastAPI, Flask, Django (DRF, Channels, Celery), Node.js (Express), Socket.io, WebRTC/mediasoup}
\cvitem{Frontend}{React.js, Next.js, Vue.js, Tailwind CSS, ShadCN, Electron}
\cvitem{Databases}{PostgreSQL, MySQL, MongoDB, SQL Server, SQLite}
\cvitem{DevOps \& Cloud}{Docker, CI/CD (GitHub Actions), Linux/VPS, Apache, Nginx, PM2, FFmpeg}
\cvitem{Cloud Platforms}{GCP (Cloud Run, Vertex AI, GKE, Storage, APIs), Azure (APIs, VPS), OVH, Alibaba Cloud}
\cvitem{Methodologies}{OOP, Design Patterns, Git/GitHub, Agile/Scrum, RBAC, JWT, Monorepo (Turborepo)}
\cvitem{Soft Skills}{Analytical Thinking, Complex Problem Solving, Systems Thinking, Fast Learner in Emerging Technologies, Cross-functional Collaboration, Research \& Literature Analysis}
\cvitem{Leadership}{Technical Leadership in AI Projects, Architecture Decision-Making, Technology \& Model Selection, Mentoring Junior Developers, End-to-End AI Project Management, Aligning AI Solutions with Real-World Problems}

% EXPERIENCE
\section{Professional Experience}

\cventry{Feb. 2026 -- Present}{AI Software Engineer \& System Architect}{Badis.ai}{Algiers, Algeria (Part-time)}{}{%
\begin{itemize}
  \item Designed and developed the full architecture of an AI-powered LMS (ML/LLM pipelines, APIs, database design).
  \item Deployed AI services into production and optimized their performance.
  \item Led system and technical architecture decisions.
\end{itemize}}

\cventry{Feb. 2026 -- Present}{AI Research Engineer — Genomic Medicine \& Precision Oncology}{Institut Pasteur of Algeria}{Algiers, Algeria (Hybrid)}{Final-year research internship}{%
\begin{itemize}
  \item End-to-end AI pipeline: patient DNA $\rightarrow$ cancer type prediction $\rightarrow$ therapeutic recommendation $\rightarrow$ automated medical report generation.
  \item Designed AI models for genomic variant analysis, cancer classification, and clinical decision support.
  \item Collaborated with researchers and engineers in a real-world biomedical context (bioinformatics, medical AI).
  \item Technologies: Python, PyTorch, Deep Learning, Genomics AI, LLMs, medical data processing.
\end{itemize}}
\newpage
\cventry{Aug. 2025 -- Jan. 2026}{AI Consultant}{Badis.ai}{Algiers, Algeria}{}{%
\begin{itemize}
  \item \textbf{AI Audit \& Advisory}: Feasibility assessment and planning of an adaptive educational AI system for the ActivMath platform.
  \item \textbf{Architecture}: Designed a personalized recommendation and learning-tracking pipeline (Python microservices, REST APIs, ONNX).
  \item \textbf{Integration}: Deployed the solution within the existing ecosystem (Flask/Next.js) on a self-managed VPS.
\end{itemize}}

\cventry{2025--2026}{Software Engineer (Contract)}{Direction Générale des Douanes}{Algeria}{}{%
\begin{itemize}
  \item \textbf{Project 1 (2025):} Developed a mail and correspondence management system for an Algerian Customs state office. Full-stack: REST API (Express.js) + React frontend; role-based access control.
  \item \textbf{Project 2 (2026):} Implemented a software for corruption risk mapping (\emph{Cartographie des risques de corruption}) for the General Directorate of Customs.
\end{itemize}}

\cventry{Jun. -- Sep. 2025}{Full-Stack Developer}{Kleerinfinit}{Algiers, Algeria}{}{%
\begin{itemize}
  \item Built a multi-tenant B2B SaaS platform using Django 5, DRF, Django Channels (WebSockets), and Celery.
  \item Designed a RESTful API with JWT authentication, RBAC role management, and analytics dashboards.
  \item Collaborated in a team of 5 developers (Agile, code reviews, bi-weekly sprints).
\end{itemize}}

\cventry{2025}{Mentor — Bootcamp (10 Days) ``CodeCraft AI to FullStack''}{FormationTech}{Algeria}{}{%
\begin{itemize}
  \item Mentored \textbf{70+ participants} in AI and Full-Stack development during intensive bootcamps.
  \item Supervised \textbf{48-hour project development cycles} evaluated by academic juries; deployed an AI resource platform.
\end{itemize}}

\cventry{2026}{Mentor — Bootcamp (13 Days) ``BitUp''}{}{Algeria}{}{%
\begin{itemize}
  \item Mentored \textbf{50+ participants} in AI and Full-Stack development during intensive bootcamps.
  \item Supervised \textbf{48-hour project development cycles} evaluated by academic juries; deployed an AI resource platform.
\end{itemize}}

\cventry{2023--2025}{AI \& Full-Stack Developer (Freelance)}{}{}{}{%
\begin{itemize}
  \item Built segmentation and classification pipelines for medical images (U-Net, YOLOv8, LinkNet, PSPNet); integrated into web interfaces (Flask, React.js).
  \item Delivered various client projects: e-commerce (Laravel/Vue.js), desktop management tools (Electron/SQLite), REST APIs.
\end{itemize}}

\cventry{2024--2025}{Head of Development Department — DevUp Club}{University of Boumerdès}{}{}{%
\begin{itemize}
  \item Led a community of \textbf{120+ developers}, organizing AI, Web, and Mobile training programs.
  \item Coordinated multiple technical projects and upskilled members through structured learning sessions.
\end{itemize}}

\cventry{2023--2024}{President of the Computer Science Club — GDSC (Google Developer Student Club)}{University of Boumerdès}{}{}{%
\begin{itemize}
  \item Led a \textbf{300+ member tech community}, organizing hackathons, workshops, and university partnerships.
  \item Drove technical engagement and community growth through large-scale events and training programs.
\end{itemize}}

\cventry{2024--2026}{Mentoring \& Technical Outreach}{}{}{Personal activity}{%
\begin{itemize}
  \item Mentored in \textbf{20+ workshops} and \textbf{6 training programs} on AI, Computer Vision, and Full-Stack development.
  \item Facilitated and co-organized \textbf{7 hackathons}.
  \item Served as jury member for \textbf{40+ teams} across 3 hackathons and final graduation project presentations.
\end{itemize}}

\cventry{2023--2024}{Medical AI Projects}{University of Boumerdès / CHU Mustapha Bacha}{}{}{%
\begin{itemize}
  \item Skin cancer classification (CNN + Vision Transformers) — \textbf{93\,\% accuracy}.
  \item Automated cell detection and counting (YOLOv8); malaria detection.
  \item Full medical diagnostic pipeline: preprocessing $\rightarrow$ inference $\rightarrow$ web interface.
\end{itemize}}

% SELECTED PROJECTS
\section{Selected Projects}
\cventry{2026}{Founder \& Lead}{SmartADN}{}{AI Genomic Analysis Startup}{%
\begin{itemize}
  \item Founded a multi-agent genomic analysis platform automating the full genetic variant interpretation pipeline: from sequencing data to structured clinical report generation.
  \item Combines bioinformatics, AI, and biomedical knowledge bases (genomics, precision medicine, clinical AI).
  \item Technologies: LangGraph, HuggingFace Transformers, Python.
\end{itemize}}
\newpage
\cventry{2026}{End-to-End Technical Plan Automation Pipeline}{}{}{Open-source only}{%
\begin{itemize}
  \item Built a fully open-source pipeline that reads a technical PDF plan, auto-generates CAD drawings, identifies suppliers, calculates TCO, produces a business plan, and outputs a multi-format catalog — end-to-end with no proprietary dependencies.
\end{itemize}}
\cventry{2025}{Real-Time Multiplayer Game with Voice Chat}{}{}{Personal project — WebRTC/mediasoup, Socket.io}{%
\begin{itemize}
  \item End-to-end development of a real-time multiplayer game with integrated voice chat.
  \item Multi-room architecture with dynamic role and vocal permission management (RBAC).
  \item Designed and led a real-time system handling \textbf{218K+ requests in 3 hours} under constrained infrastructure (VPS: 2 vCPUs / 2\,GB RAM).
\end{itemize}}

\cventry{2024}{Multi-Vendor Marketplace}{}{}{Turborepo monorepo, Next.js, Node.js}{%
\begin{itemize}
  \item Full-stack marketplace with monorepo architecture (Turborepo); multi-vendor management, shared packages.
\end{itemize}}

\cventry{2023}{FFmpeg-Optimized Streaming Platform}{}{}{Node.js, FFmpeg, React}{%
\begin{itemize}
  \item Engineered a streaming platform with adaptive video encoding (FFmpeg), supporting \textbf{1,500 concurrent users} and ensuring system stability under load.
\end{itemize}}

\cventry{2022}{Co-Founder \& Lead}{Résumily}{}{Academic summarization platform}{%
\begin{itemize}
  \item Scaled a student platform to \textbf{10,000+ monthly users}; secured an official partnership with the Computer Science department.
  \item Grew team from \textbf{13 to 43 members in 2 months}, demonstrating rapid team scaling and leadership.
  \item Led to nomination as GDSC Lead (Google Developer Student Club, 300 members).
\end{itemize}}


% EARLY WORK
\section{Early Work}
\cventry{2021}{5 Management Information Systems}{BTS Final Projects — INSFP Hamdi Ben Yahia}{}{Delphi/Embarcadero}{%
Stock, HR, Accounting, Library, and Academic Internship Management — complete desktop software delivered during BTS program.}

% RESEARCH
\section{Research \& Publications}
\cvitem{Published Paper}{\textbf{An End-to-End Approach for SNV Pathogenicity Prediction via Progressive Fine-Tuning of Nucleotide Transformer-v2} — \underline{Benhenni Ouahabi}, Djamel Gaceb, Fayçal Touazi, Wissal Kebour, Rayane Chakib Idris, Belkacem Rouibi, Anis Ismail. LIMOSE Laboratory, Univ. M'hamed Bougara, Boumerdès, Algeria. Published \& presented at national conference.}
\cvitem{GenAI Project}{\emph{Local Retrieval-Augmented Generation System} — document ingestion pipeline (PDF, DOCX, Markdown), vector search with embeddings, LLM inference via Ollama; fully local deployment with no external API.}
\cvitem{Paper submitted}{Melanoma classification using Deep Learning (CNN \& Vision Transformers) — submitted for peer review.}

% EDUCATION
\section{Education}
\cventry{Jun. 2026}{Master's in Computer Science — Information Systems}{University of Boumerdès (UMBB)}{}{}{}
\cventry{2024}{Bachelor's in Computer Science — Information Systems}{University of Boumerdès (UMBB)}{}{}{}
\cventry{2018--2021}{Higher Technician in Database Administration}{INSFP Hamdi Ben Yahia}{}{}{}
\cventry{2021}{Baccalaureate — Mathematics}{Bouira}{}{}{}
\cventry{2023--2024}{AI Certifications (Computer Vision, NLP, LLM)}{Kaggle · Udemy · Hugging Face}{}{}{}

% LANGUAGES
\section{Languages}
\cvitem{Arabic}{C2 — Native} \cvitem{French}{C1} \cvitem{English}{B2}
\end{document}
